---
title: "Homework 1"
author: Yanhao Li
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r create_df}
prob1_df =
  tibble(
    random_sample = rnorm(10),
    random_sample_gt_0 = random_sample > 0,
    character_vector = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vector = factor(c("low", "low", "high", "mod", "high", "mod", "low", "low", "low", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, random_sample))
mean(pull(prob1_df, random_sample_gt_0))
mean(pull(prob1_df, character_vector))
mean(pull(prob1_df, factor_vector))
```

I can take the mean of numbers and logical but not character or factor.

Convert variables from one type to another.

```{r try_numeric}
as.numeric(pull(prob1_df, random_sample_gt_0))
as.numeric(pull(prob1_df, character_vector))
as.numeric(pull(prob1_df, factor_vector))
```

I can convert the variables of logical and factor but not character. 

R treat "FALSE" as 0 and "TRUE" as 1. It could sometimes assign numbers to factor levels. This helps explain what happens when I take the mean. 

Convert logical vector, and multiply the random sample by the result.

```{r convert_multiply}
as.numeric(pull(prob1_df, random_sample_gt_0))*pull(prob1_df, random_sample)
as.factor(pull(prob1_df, random_sample_gt_0))*pull(prob1_df, random_sample)
as.numeric(as.factor(pull(prob1_df, random_sample_gt_0)))*pull(prob1_df, random_sample)
```


## Problem 2

Load the penguins dataset. 

```{r load_dataset}
data("penguins", package = "palmerpenguins")
```

The short description of the penguins dataset:

It includes important variables named as `r colnames(penguins)`. 

The range of bill length is `r max(pull(penguins, bill_length_mm), na.rm = TRUE) - min(pull(penguins, bill_length_mm), na.rm = TRUE)` mm.

The range of bill depth is `r max(pull(penguins, bill_depth_mm), na.rm = TRUE) - min(pull(penguins, bill_depth_mm), na.rm = TRUE)` mm.

The range of flipper length is `r max(pull(penguins, flipper_length_mm), na.rm = TRUE) - min(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

The range of body mass is `r max(pull(penguins, body_mass_g), na.rm = TRUE) - min(pull(penguins, body_mass_g), na.rm = TRUE)` g.

It has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

Create the dataframe containing variables for scatterplot.

```{r df_create}
set.seed(1234)

plot_df = tibble(
  x_bl = pull(penguins, bill_length_mm),
  y_fl = pull(penguins, flipper_length_mm)
)
```

Plot the scatterplot of `y_fl` vs `x_bl`. 

```{r yx_scatter}
ggplot(plot_df, aes(x = x_bl, y = y_fl, color = pull(penguins, species), na.rm = TRUE)) + geom_point()
```

Export scatterplot to project directory.

```{r}
ggsave(file="penguins.pdf")
```

